Automating Verification of MPC Security

### 2023-06-09 popl24/hyperprop.tex
checkpoint

In this section we formulate a new hyperproperty that we show is sound
for passive security in the real/ideal model, called
\emph{noninterference modulo output ($\NIMO$)}. We do not claim
completeness with respect to passive security, but soundness
guarantees that enforcement of $\NIMO$ in our analyses implies passive
security. In Section \ref{section-bruteforce} we show how $\NIMO$ can
be automatically enforced in a brute-force manner, and in Section
\ref{section-composition} we show how $\NIMO$ can be refined to obtain
compositional properties that can be verified in a scalable manner for
protocols that incorporate modular sub-protocols, with a
specific use-case of Yao's Garbled Circuits (YGC) as an example.
The latter methodology demonstrates a particular advantage of our
hyperproperty formulation.

\subsection{Passive Security and the Real/Ideal Model} The traditional
security model of MPC is formulated by positing a \emph{simulator}
that exists in the ideal world, and is trying to reconstruct
observable information in a real world run of a protocol $\prog$ that
correctly implements an ideal functionality $\idealf$- that is,
execution of a configuration $(\store,\prog)$. We will assume that any
protocol $\prog$ includes a public \emph{output view} $x$ where the
result is published. The protocol is \emph{correct} iff the resulting
memory contains $x \mapsto \idealf(\store_S)$, where $S$ are the
secret inputs (honest and corrupt) in $\prog$.

The simulator is given just the corrupt inputs to the run- that is,
$\store_{S_C}$- and the output of the protocol- that is,
$\idealf(\store)$- and tries to reconstruct the \emph{distribution of
adversarial views} observed in the real world. The intuition here is
that the simulator is given the information that is necessarily
available to the adversary by observing a run of the protocl, and if
the simulator can reconstruct whatever information appears in the real
world adversarial views, by reconstructing their distributions, then
those views leak no additional information, i.e., \emph{have no
additional dependencies on honest input secrets than what is revealed
by the output and conditionings on corrupt inputs}.

@@

Then we can define passive security in the real/ideal
model as follows. One detail here is the assumption of an
\emph{honest majority} which is a standard bound on the
capabilities of the adversary in this threat model.
\begin{definition}[Passive Security]
  Assume given a program $\prog$ that correctly implements an ideal
  functionality $\idealf$, with $\iov(\prog) = (S,V)$.  Then $\prog$
  is \emph{passive secure in the simulator model} iff for all
  partitions of the federation into honest and corrupt sets $H$ and $C$
  with $|C| < |H|$ and for all $\store \in \mems(S)$ there exists a
  simulation $\SIM_C$ such that:
  $$
  \progd(\SIM_C(\store_{S_C},\idealf(\store))) = \margd{(\condd{\progd(\prog)}{\store})}{V_C}
  $$
\end{definition}

\subsection{Probabilistic Noninterference} The discussion above suggests a
security semantics- that is, a hyperproperty- analagous to
noninterference in a probabilistic setting. First, let's
define low equivalence of memories in the current setting:
\begin{definition}[Memory Low Equivalence]
  Given $\store^1$ and $\store^2$ with $\dom(\store^1) = \dom(\store^2) = X$,
  we write $\store^1 =_C \store^2$ iff $\store^1_{X_C} = \store^2_{X_C}$.
\end{definition}
Now, we can define probabilistic noninterference as a property of
programs ensuring that low-equivalent initial memories produce
the same low-observable trace (i.e., corrupt views) \emph{with the
same probability}. 
\begin{definition}[Probabilistic Noninterference]
  Given a program $\prog$ with $\iov(\prog) = (S,V)$, we say that
  $\prog$ satisfies \emph{probabilistic noninterference} iff for all
  $\store_1, \store_2 \in \mems(S)$:
  $$\store_1 =_C \store_2 \implies
    \margd{(\condd{\progd(\prog)}{\store_1})}{V_C} =
    \margd{(\condd{\progd(\prog)}{\store_2})}{V_C}$$
\end{definition}

An important consequence of probabilistic noninterference refines an
idea we introduced in Lecture Notes 12, which is that noninterering
programs do not improve adversarial knowledge about secrets.
More precisely, in $\fedcat$ the initial probability of a correct
guess by the adversary is the marginal distribution of honest secrets
in the program distribution conditioned by corrupt inputs.
The final (and thus best, due to monotonicity) adversarial
knowledge is also the marginal distribution of honest secrets in the
program distribution, but conditioned by corrupt inputs \emph{and}
corrupt views. Noninterference in the probabilistic setting implies
that these are the same.
\begin{lemma}
  Given a program $\prog$ with $\iov(\prog) = (S,V)$, 
  $\prog$ satisfies probabilistic noninterference iff for all
  $\store \in \mems(S \cup V)$:
  $$\margd{(\condd{\progd(\prog)}{\store_{S_C}})}{S_H} =
    \margd{(\condd{\progd(\prog)}{\store_{(S\cup V)_C}})}{S_H} $$
\end{lemma}

>>>>

In this section we formulate a new hyperproperty that we show is sound
for passive security in the real/ideal model, called
\emph{noninterference modulo output ($\NIMO$)}. We do not claim
completeness with respect to passive security, but soundness
guarantees that enforcement of $\NIMO$ in our analyses implies passive
security. In Section \ref{section-bruteforce} we show how $\NIMO$ can
be automatically enforced in a brute-force manner, and in Section
\ref{section-composition} we show how $\NIMO$ can be refined to obtain
compositional properties supporting efficient, scalable enforcement of
complex protocols that incorporate modular subprotocols, with a
specific use-case of Yao's Garbled Circuits (YGC) as an example where
garbled gates are the compositional units.  The latter methodology
demonstrates a particular advantage of our hyperproperty formulation.

\subsection{Passive Security and the Real/Ideal Model} Here we
briefly summarize the formal definition of MPC security. For a
more detailed discussion the reader is referred to \cite{XXX}.
In this paper we will consider the \emph{passive} aka
semi-honest aka honest-but-curious variant. In this threat
model, protocol participants can be corrupted, but all clients
follow the rules of the protocol- as opposed to the
\emph{active} aka maliciouos variant where participants
are allowed to break these rules. In the passive model, the
vulnerability is through information leaked to the adversary
through the views of corrupted participants. While the passive
model also assumes that any clients can potentially be
corrupted, it assumes that no more than half will be-
i.e., it assumes an \emph{honest majority}.

The real/ideal model posits a \emph{simulator} that exists in an ideal
world, whose goal is to reconstruct observable information in a real
world run of a protocol $\prog$ that correctly implements an ideal
functionality $\idealf$- that is, execution of a configuration
$\config{\store}{\prog}$. We will assume that any protocol $\prog$
includes a public \emph{output view} $\outv$ where the result is
published, where $0$ is the ``public'' client and thus $\outv$
is of the form $\vx{0}{w}$ for some $w$, i.e., is owned by 0.
Cl
Note that the protocol is \emph{correct} iff the resulting
memory contains $\outv \mapsto \idealf(\store_S)$, where $S$ are the
secret inputs (honest and corrupt) in $\prog$.

The simulator is given just the corrupt inputs to the run- that is,
$\store_{S_C}$- and the output of the protocol- that is,
$\idealf(\store)$- and tries to reconstruct the \emph{distribution of
adversarial views} observed in the real world. The intuition here is
that the simulator is given the information that is necessarily
available to the adversary by observing a run of the protocl, and if
the simulator can reconstruct whatever information appears in the real
world adversarial views, by reconstructing their distributions, then
those views leak no additional information, i.e., they have no
additional dependencies on honest input secrets than what is revealed
by the output and conditionings on corrupt inputs.

@@

Then we can define passive security in the real/ideal
model as follows. 
\begin{definition}[Passive Security]
  Assume given a program $\prog$ that correctly implements an ideal
  functionality $\idealf$, with $\iov(\prog) = (S,V)$.  Then $\prog$
  is \emph{passive secure in the simulator model} iff for all
  partitions of the federation into honest and corrupt sets $H$ and $C$
  with $|C| < |H|$ and for all $\store \in \mems(S)$ there exists a
  simulation $\SIM_C$ such that:
  $$
  \progd(\SIM_C(\store_{S_C},\idealf(\store))) = \margd{(\condd{\progd(\prog)}{\store})}{V_C}
  $$
\end{definition}

\subsection{Probabilistic Noninterference} Previous work has noted
relations between probabilistic noninterference and security
properties such as memory trace obliviousness \cite{XXX} and passive
security \cite{XXX}. And above (Section \ref{section-pmf-examples}) we
have demonstrated that our basic encryption scheme enjoys a noninterference
property. To formulate probabilistic noninterference in
our setting we begin by defining low equivalence of memories.
\begin{definition}[Memory Low Equivalence]
  Given $\store^1$ and $\store^2$ with $\dom(\store^1) = \dom(\store^2) = X$,
  we write $\store^1 =_C \store^2$ iff $\store^1_{X_C} = \store^2_{X_C}$.
\end{definition}
Now, we can define probabilistic noninterference as a property of
programs ensuring that low-equivalent initial memories produce
the same low-observable trace (i.e., corrupt views) \emph{with the
same probability}. 
\begin{definition}[Probabilistic Noninterference]
  Given a program $\prog$ with $\iov(\prog) = (S,V)$, we say that
  $\prog$ satisfies \emph{probabilistic noninterference} iff for all
  $\store_1, \store_2 \in \mems(S)$:
  $$\store_1 =_C \store_2 \implies
    \margd{(\condd{\progd(\prog)}{\store_1})}{V_C} =
    \margd{(\condd{\progd(\prog)}{\store_2})}{V_C}$$
\end{definition}

Despite the intuitive resonance between noninterference
and passive security, since MPC
protocols implement an ideal functionality, they cannot generally satisfy
noninterference. We can easily demonstrate this by using
Example \ref{example-he} as a failure witness, where we'll
assume $C = \{0,2\}$ and $H = \{1,3\}$:
$$
(\progd(\prog_{\ref{example-he}}))({\outv \mapsto 1}|\{\{\sx{1}{1} \mapsto 0, \sx{2}{1} \mapsto 1, \sx{3}{1} \mapsto 0 \} \})
= 1
$$
whereas:
$$
(\progd(\prog_{\ref{example-he}}))({\outv \mapsto 1}|\{\{\sx{1}{1} \mapsto 1, \sx{2}{1} \mapsto 1, \sx{3}{1} \mapsto 0 \} \})
= 0
$$

Probabilistic noninterference can also be restated to formally capture a
basic intuition that noninterfering programs do not provide
the adversary with any clues about honest secrets through corrupt
views, as in the following Lemma. This is similar to asserting that
adversarial knowledge is not increased by the execution of a program as in formulations
of so-called gradual release \cite{XXX}. 
\begin{lemma}
  Given a program $\prog$ with $\iov(\prog) = (S,V)$, 
  $\prog$ satisfies probabilistic noninterference iff for all
  $\store \in \mems(S \cup V)$:
  $$\margd{(\condd{\progd(\prog)}{\store_{S_C}})}{S_H} =
    \margd{(\condd{\progd(\prog)}{\store_{(S\cup V)_C}})}{S_H} $$
\end{lemma}
